Hybrid Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-08-12 manuscript/main.tex
W recursive

	\subsubsection{Iterative step 2: residualization via hybrid-on-scalar regression} \label{section:sub:residualization}
	The $l$-th iteration's second step involves residualization of both predictors and responses. We first compute the individual PLS score:  
	\begin{equation}\label{def:plsscore}
		\hat{\rho}^{[l]}_i := \langle \widetilde{W}_i^{[l]}, \, \hat{\xi}^{[l]} \rangle_{\mathcal{H}},
	\end{equation}
	using the estimated PLS component direction $\widehat{\xi}^{[l]}$ obtained from Propositions \ref{proposition:eigen_regul} and \ref{proposition:linear_regul}. 
	Since   $\widetilde{W}_i^{[l]}$ are assumed to have a sample mean of zero, these PLS scores will also have a sample mean of zero.
	To obtain the $(l+1)$-th  iteration's responses and hybrid predictors, we regress the $(l)$-th iteration's responses and hybrid predictors on  
 these PLS scores by least squares and then residualize. 
	Specifically,
the $(l+1)$-th predictor is computed as a hybrid-on-scalar linear regression residual.
In the same spirit as the PLS component direction estimation step,
rather than treating the hybrid object as a long vector of concatenated function evaluations at time points and scalar vectors,
we employ a basis expansion approach to fit the entire hybrid object in one step.
Therefore, our method is computationally efficient, applicable for dense or irregular functional data, and keeps the residual smooth, as it enforces the regression coefficient, $\delta^{[l]}$, as an element of $\tilde{\mathcal{H}}$ as defined in Equation \eqref{def:truncated_hilbert_space}.
	Consequently, $\delta^{[l]}$ is obtained by minimizing a  
	least squares criterion:
	\begin{equation}\label{def:argmin_pensse}
		\hat{\delta}^{[l]} := \arg \min_{\delta \in \tilde{\mathcal{H}}} \sum_{i=1}^n 
		\| \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta\|_{\mathcal{H}}^2.
	\end{equation}
  On the other hand, the $(l+1)$-th response   is computed as a scalar-on-scalar linear regression residual. 
 The following proposition demonstrates that this residualization step can be performed simply, analogous to scalar PLS.
	\begin{lemma}[Closed-form  solution]\label{proposition:closed_form_orthgonalization}
		Let us denote
		$
		\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top.
		%\quad\text{and} \quad		\bar{\rho}^{[l]} := (\hat{\boldsymbol{\rho}}^{[l]})^\top \hat{\boldsymbol{\rho}}^{[l]}.
		$
	The $(l+1)$-th iteration's  predictors and responses are   computed as:
\begin{equation}\label{algorithm_step:residualization_predictor}
	\widetilde{W}_i^{[l+1]} 
	= 
	\widetilde{W}_i^{[l]}  - 
	\frac{\widehat{\rho}_{il}}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
	\sum_{i=1}^n 
	\widehat{\rho}_{il}
	\widetilde{W}_i^{[l]},
	%%%%%%%%%%% 
	\quad 
	Y_i^{[l+1]} := Y_i^{[l]} - 
	\frac{
		\mathbf{y}^{[l] \top }  \hat{\boldsymbol{\rho}}^{[l]}
	}{
		\| \hat{\boldsymbol{\rho}}^{[l]} \|_2^2
	}
	\widehat{\rho}_{il}.
\end{equation} 	
	\end{lemma}
	Proof of Lemma \ref{proposition:closed_form_orthgonalization} is provided in Appendix \ref{section:proof:proposition:closed_form_orthgonalization}.
	\jongmin{proof needs to be revised}
Since $\widetilde{W}_i^{[l]}$ and $Y_i^{[l]}$ are assumed to have a sample mean of zero, their respective residuals, $\widetilde{W}_i^{[l+1]}$ and $Y_i^{[l+1]}$, also maintain a zero sample mean.

@@

		Our next task is to show that 
		$
		\Theta^{[l_1] }
		\mathbb{B}
		\hat{\boldsymbol{\xi}}_{l_2} = \mathbf{0} \in \mathbb{R}^n.
		$
		From the construction in \eqref{def:full_theta}, \eqref{def:theta} and \eqref{def:gram_block}, the
		$i$th entry of $\Theta^{[l_1] }
		\mathbb{B}
		\hat{\boldsymbol{\xi}}_{l_2}$ 
		is
		\begin{align*}
			(\Theta^{[l_1] }
			\mathbb{B}
			\hat{\boldsymbol{\xi}}_{l_2})_i
			&=
			(\theta_{i11}^{[l_1]}, \ldots, \theta_{i1M}^{[l_1]}, \ldots, \theta_{iK1}^{[l_1]}, \ldots, \theta_{iKM}^{[l_1]}, Z_{i1}^{[l_1]}, \ldots, Z_{ip}^{[l_1]})
			\mathbb{B}
			\hat{\boldsymbol{\xi}}_{l_2}
			%%%%%%%%%%%%%%%%%%%%%%%%%%%
			\\&=
			\sum_{k=1}^K
			\boldsymbol{\theta}_{ik}^{[l_1]} B
			\hat{\boldsymbol{\gamma}}_k^{[l_2]}
			+
			\mathbf{Z}_{i}^{[l_1] \top } \hat{\boldsymbol{\zeta}}^{[l_2]}
			%%%%%%%%%%%%%%%%%%%%%%%%%%%
			\\	&=
			\langle
			\widetilde{W}_i^{[l_1]}, 
			\hat{\xi}^{[l_2]}
			\rangle_{\mathcal{H}},
		\end{align*}
where the last equality uses the computation of the $i$th entry in \eqref{score_inner_product_all_n}. To expand the last quantity, we use a recursive relationship derived as follows.
\begin{align*}
	\widetilde{W}_i^{[l_1]} &= \widetilde{W}_i^{[l_1-1]} - \widehat{{\rho}}_i^{[l_1-1]} \widehat{\delta}^{[l_1-1]}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\\&\overset{(i)}{=}
	\widetilde{W}_i^{[l_1-1]}
	-
	\frac{\widehat{{\rho}}_i^{[l_1-1]}}{\| \widehat{\boldsymbol{\rho}}^{[l_1-1]} \|_2^2}
	\bigl(
	\sum_{k=1}^K {\Theta}_{k}^{[l_1-1]} 
	+
	Z^{[l_1-1]} 
	\bigr)
	\widehat{\boldsymbol{\rho}}^{[l_1-1]}
	\\&=
	\langle
	\widetilde{W}_i^{[l_1-1]}  , 
	\hat{\xi}^{[l_2]}
	\rangle_{\mathcal{H}}
	-
	\frac{\widehat{{\rho}}_i^{[l_1-1]}}{\| \widehat{\boldsymbol{\rho}}^{[l_1-1]} \|_2^2}
	\widehat{\boldsymbol{\rho}}^{[l_1-1] \top}
	\langle
	\widetilde{W}^{[l_1-1]}  , 
	\hat{\xi}^{[l_2]}
	\rangle_{\mathcal{H}}
\end{align*}
Using the regression model  we used for residualization,
		and step $(iii)$ uses 
		the closed-form formula of $\widehat{\delta}^{[l_1-1]}$ given by Lemma \ref{proposition:closed_form_orthgonalization},
		and we abuse the notation as
		$\langle
		\widetilde{W}_1^{[l_1-1]}  , 
		\hat{\xi}^{[l_2]}
		\rangle_{\mathcal{H}}:=
		\bigl(
		\langle
		\widetilde{W}_n^{[l_1-1]}  , 
		\hat{\xi}^{[l_2]}
		\rangle_{\mathcal{H}},
		\ldots,
		\langle
		\widetilde{W}^{[l_1-1]}  , 
		\hat{\xi}^{[l_2]}
		\rangle_{\mathcal{H}}
		\bigr)^\top \in \mathbb{R}^n.
		$

		Therefore, we have
		\begin{equation*}
			\Theta^{[l_1] }
			\mathbb{B}
			\hat{\boldsymbol{\xi}}_{l_2}
			=
			\langle
			\widetilde{W}^{[l_1-1]}  , 
			\hat{\xi}^{[l_2]}
			\rangle_{\mathcal{H}}
			-
			\frac{1}{\| \widehat{\boldsymbol{\rho}}^{[l_1-1]} \|_2^2}
			\widehat{\boldsymbol{\rho}}^{[l_1-1] \top}
			\langle
			\widetilde{W}^{[l_1-1]}  , 
			\hat{\xi}^{[l_2]}
			\rangle_{\mathcal{H}}
			\widehat{\boldsymbol{\rho}}^{[l_1-1]}
		\end{equation*}
		\begin{equation*}
			\hat{\boldsymbol{\pi}}_j^{[l]}
			=
			\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
			\Theta_j^{[l] \top}
			\hat{\boldsymbol{\rho}}^{[l]}
			,
			~
			j = 1, \ldots, K,
		\end{equation*}
		and scalar parts given by:
		\begin{equation*}
			\hat{\boldsymbol{\chi} }^{[l]}
			=
			(\mathbf{Z}^{[l]})^\top  \hat{\boldsymbol{\rho}}^{[l]}.
		\end{equation*}

	which, after applying the finite-dimensional form (9), implies that
	\begin{align*}
		\widetilde{C}^{*[l]}B^*[\mathbf{t}] &=\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1}\widehat{\boldsymbol{\gamma}}^*_{l-1}B^*[\mathbf{t}] \\
		&= \widetilde{C}^{*[l-1]}B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top \widetilde{C}^{*[l-1]} J^\ast \left(\widehat{\boldsymbol{\rho}}_{i,l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1} J^\ast \right)^{-1} B^*[\mathbf{t}] \\
		& =\widetilde{C}^{*[l-1]}B^*[\mathbf{t}] -  \left(\frac{\widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \right) \widetilde{C}^{*[l-1]} B^*[\mathbf{t}] \\
		&= \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \right) \widetilde{C}^{*[l-1]} B^*[\mathbf{t}].
	\end{align*}

	Thus, we have
	\begin{align*}
		\widetilde{W}^{[l]}[\mathbf{t}] &= \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \right) \widetilde{W}^{[l-1]}[\mathbf{t}] \\
		&= \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{l-1} \widehat{\boldsymbol{\rho}}_{l-1}^\top}{\widehat{\boldsymbol{\rho}}_{l-1}^\top \widehat{\boldsymbol{\rho}}_{l-1}} \right) \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{l-2} \widehat{\boldsymbol{\rho}}_{l-2}^\top}{\widehat{\boldsymbol{\rho}}_{l-2}^\top \widehat{\boldsymbol{\rho}}_{l-2}} \right) \widetilde{W}^{[l-2]}[\mathbf{t}] \\
		&= P \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right)\widetilde{W}^{[j]}[\mathbf{t}]
	\end{align*}
	where $P$ is an $n \times n$ matrix defined as
	\begin{equation*}
		P = \prod \limits_{h=j+1}^{l-1} \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{h} \widehat{\boldsymbol{\rho}}_{h}^\top}{\widehat{\boldsymbol{\rho}}_{h}^\top \widehat{\boldsymbol{\rho}}_{h}} \right)
	\end{equation*}
	Then for $j < l$,
	\begin{align*}
		\int_{\mathcal{T}} \widetilde{W}^{[l]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} &= \int_{\mathcal{T}} P   \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right)\widetilde{W}^{[j]}[\mathbf{t}]  \widehat{\xi}_k[\mathbf{t}] d\mathbf{t}  \\
		&= P \left\{\int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} \right\} \\ 
		&=P \left( \widehat{\boldsymbol{\rho}}_j - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \widehat{\boldsymbol{\rho}}_j \right) \\
		&= P(\widehat{\boldsymbol{\rho}}_j-\widehat{\boldsymbol{\rho}}_j) \\
		&= \mathbf{0} \in \mathbb{R}^n, 
	\end{align*}
	noting that $\int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} = \widehat{\boldsymbol{\rho}}_j$. Now by the , we have that

@@

	\section{Proof of Proposition \ref{proposition: orthnormality of PLS scores}}\label{section:proof:proposition: orthnormality of PLS scores}

>>>>

	\subsubsection{Iterative step 2: residualization via hybrid-on-scalar regression} \label{section:sub:residualization}
	The $l$-th iteration's second step involves residualization of both predictors and responses. We first compute the individual PLS score:  
	\begin{equation}\label{def:plsscore}
		\hat{\rho}^{[l]}_i := \langle \widetilde{W}_i^{[l]}, \, \hat{\xi}^{[l]} \rangle_{\mathcal{H}},
	\end{equation}
	using the estimated PLS component direction $\widehat{\xi}^{[l]}$ obtained from Propositions \ref{proposition:eigen_regul} and \ref{proposition:linear_regul}. 
	Since   $\widetilde{W}_i^{[l]}$ are assumed to have a sample mean of zero, these PLS scores will also have a sample mean of zero.
	To obtain the $(l+1)$-th  iteration's responses and hybrid predictors, we regress the $(l)$-th iteration's responses and hybrid predictors on  
 these PLS scores by least squares and then residualize. 
	Specifically,
the $(l+1)$-th predictor is computed as a hybrid-on-scalar linear regression residual.
In the same spirit as the PLS component direction estimation step,
rather than treating the hybrid object as a long vector of concatenated function evaluations at time points and scalar vectors,
we employ a basis expansion approach to fit the entire hybrid object in one step.
Therefore, our method is computationally efficient, applicable for dense or irregular functional data, and keeps the residual smooth, as it enforces the regression coefficient, $\delta^{[l]}$, as an element of $\tilde{\mathcal{H}}$ as defined in Equation \eqref{def:truncated_hilbert_space}.
	Consequently, $\delta^{[l]}$ is obtained by minimizing a  
	least squares criterion:
	\begin{equation}\label{def:argmin_pensse}
		\hat{\delta}^{[l]} := \arg \min_{\delta \in \tilde{\mathcal{H}}} \sum_{i=1}^n 
		\| \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta\|_{\mathcal{H}}^2.
	\end{equation}
  On the other hand, the $(l+1)$-th response   is computed as a scalar-on-scalar linear regression residual. 
 The following proposition demonstrates that this residualization step can be performed simply, analogous to scalar PLS.
	\begin{lemma}[Closed-form  solution]\label{proposition:closed_form_orthgonalization}
		Let us denote
		$
		\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top.
		%\quad\text{and} \quad		\bar{\rho}^{[l]} := (\hat{\boldsymbol{\rho}}^{[l]})^\top \hat{\boldsymbol{\rho}}^{[l]}.
		$
	The $(l+1)$-th iteration's  predictors and responses are   computed as:
\begin{equation}\label{algorithm_step:residualization_predictor}
	\widetilde{W}_i^{[l+1]} 
	:= 
	\widetilde{W}_i^{[l]}  - 
	\frac{\widehat{\rho}_{il}}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
	\sum_{i=1}^n 
	\widehat{\rho}_{il}
	\widetilde{W}_i^{[l]},
	%%%%%%%%%%% 
	\quad 
	Y_i^{[l+1]} := Y_i^{[l]} - 
	\frac{
		\mathbf{y}^{[l] \top }  \hat{\boldsymbol{\rho}}^{[l]}
	}{
		\| \hat{\boldsymbol{\rho}}^{[l]} \|_2^2
	}
	\widehat{\rho}_{il}.
\end{equation} 	
	\end{lemma}
	Proof of Lemma \ref{proposition:closed_form_orthgonalization} is provided in Appendix \ref{section:proof:proposition:closed_form_orthgonalization}.
	\jongmin{proof needs to be revised}
Since $\widetilde{W}_i^{[l]}$ and $Y_i^{[l]}$ are assumed to have a sample mean of zero, their respective residuals, $\widetilde{W}_i^{[l+1]}$ and $Y_i^{[l+1]}$, also maintain a zero sample mean.

@@

		Our next task is to show that 
		\Theta^{[l_1] }
		\hat{\boldsymbol{\xi}}_{l_2} = \mathbf{0} \in \mathbb{R}^n.
		From the construction in \eqref{def:full_theta}, \eqref{def:theta} and \eqref{def:gram_block}, the
		$i$th entry of $\Theta^{[l_1] }
		\hat{\boldsymbol{\xi}}_{l_2}$ 
		is
			(\Theta^{[l_1] }
			\hat{\boldsymbol{\xi}}_{l_2})_i
			(\theta_{i11}^{[l_1]}, \ldots, \theta_{i1M}^{[l_1]}, \ldots, \theta_{iK1}^{[l_1]}, \ldots, \theta_{iKM}^{[l_1]}, Z_{i1}^{[l_1]}, \ldots, Z_{ip}^{[l_1]})
			\hat{\boldsymbol{\xi}}_{l_2}
			%%%%%%%%%%%%%%%%%%%%%%%%%%%
			\sum_{k=1}^K
			\boldsymbol{\theta}_{ik}^{[l_1]} B
			\hat{\boldsymbol{\gamma}}_k^{[l_2]}
			\mathbf{Z}_{i}^{[l_1] \top } \hat{\boldsymbol{\zeta}}^{[l_2]}
			%%%%%%%%%%%%%%%%%%%%%%%%%%%
			\langle
			\widetilde{W}_i^{[l_1]}, 
			\hat{\xi}^{[l_2]}
			\rangle_{\mathcal{H}},
where the last equality uses the computation of the $i$th entry in \eqref{score_inner_product_all_n}. To expand the last quantity, we use a recursive relationship derived as follows. Recall from Lemma  \ref{proposition:closed_form_orthgonalization} that we have
	\begin{equation}\label{algorithm_step:residualization_predictor:recall}
	\widetilde{W}_i^{[l_1]} 
	:= 
	\widetilde{W}_i^{[l_1-1]}  - 
	\frac{\widehat{\rho}_{i\,l_1-1}}{\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2}
	\sum_{i=1}^n 
	\widehat{\rho}_{i \,l_1-1}
	\widetilde{W}_i^{[l_1-1]}.
Let us denote, with some abuse of notation:
	\widetilde{\boldsymbol{W}}^{[l_1]}  := 
	\bigl(
\widetilde{W}_1^{[l_1-1]}, \ldots, \widetilde{W}_n^{[l_1-1]}
	\bigr)^\top \in \tilde{\mathcal{H}}^{\otimes n}.
Then using \eqref{algorithm_step:residualization_predictor:recall}, we have, with some abuse of notation,
\widetilde{\boldsymbol{W}}^{[l_1]}  = 
\widetilde{\boldsymbol{W}}^{[l_1-1]} - 
	\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l_1-1]}\|_2^2}
	\hat{\boldsymbol{\rho}}^{[l_1-1] }
	\hat{\boldsymbol{\rho}}^{[l_1-1] \top
	} 
		\widetilde{\boldsymbol{W}}^{[l_1-1]},
Clearly, the right-hand side represents a linear operator from $\tilde{\mathcal{H}}^{\otimes n}$ to $\tilde{\mathcal{H}}^{\otimes n}$, which we denote as $P^{[l_1-1]}$.
	Thus, 
	we have $\widetilde{\boldsymbol{W}}^{[l_1]}  = 
	P^{[l_1-1]} \widetilde{\boldsymbol{W}}^{[l_1-1]}$.
Using this relationship, we have
		\widetilde{\boldsymbol{W}}^{[l_1]} &=P^{[l_1-1]} \widetilde{\boldsymbol{W}}^{[l_1-1]} \\
		P^{[l_1-1]} P^{[l_1-2]} \widetilde{\boldsymbol{W}}^{[l_1-2]}
		&= P^{[l_1-1]} P^{[l_1-2]} \ldots P^{[l_2 + 1]}  P^{[l_2]} \widetilde{\boldsymbol{W}}^{[l_2]}
&=P P^{[l_2]} \widetilde{\boldsymbol{W}}^{[l_2]},		
	where $P = P^{[l_1-1]} P^{[l_1-2]} \ldots P^{[l_2 + 1]} $ is a linear operator from  $\tilde{\mathcal{H}}^{\otimes n}$.
	Then for $j < l$,
		\int_{\mathcal{T}} \widetilde{W}^{[l]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} &= \int_{\mathcal{T}} P   \left(I_n - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \right)\widetilde{W}^{[j]}[\mathbf{t}]  \widehat{\xi}_k[\mathbf{t}] d\mathbf{t}  \\
		&= P \left\{\int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} \right\} \\ 
		&=P \left( \widehat{\boldsymbol{\rho}}_j - \frac{\widehat{\boldsymbol{\rho}}_{j} \widehat{\boldsymbol{\rho}}_{j}^\top}{\widehat{\boldsymbol{\rho}}_{j}^\top \widehat{\boldsymbol{\rho}}_{j}} \widehat{\boldsymbol{\rho}}_j \right) \\
		&= P(\widehat{\boldsymbol{\rho}}_j-\widehat{\boldsymbol{\rho}}_j) \\
		&= \mathbf{0} \in \mathbb{R}^n, 
	noting that $\int_{\mathcal{T}} \widetilde{W}^{[j]}[\mathbf{t}] \widehat{\xi}_j[\mathbf{t}] d\mathbf{t} = \widehat{\boldsymbol{\rho}}_j$. Now by the , we have that

@@

	\end{proof}
	\section{Proof of Proposition \ref{proposition: orthnormality of PLS scores}}\label{section:proof:proposition: orthnormality of PLS scores}
